---
title: "Alcohol vs Seat choice"
author: "Manuel Villamil"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  Based off the box plot the median of people who sit in the back consume more alcohol than the third quartile of both people in the front and  middle.
  

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
The third quartile of the fron is 2 and the third quantile of the middle is 3. The median of the back is 4 so in this case the median of the bback is higher than the third quantile of both the front and middle.
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Running the model shows that the probability of people drinking the same in the front and the middle compared to the back was 0.000116. So there's a significant difference between how much they drink.

```{r}
plot(TukeyHSD(model1))
```
## Conclusions



